\documentclass[11pt]{article}
\usepackage{scimisc-cv}
\usepackage{fontawesome5}
 \usepackage{hyperref}
 \hypersetup{
     colorlinks=true,
     linkcolor=blue,     
     urlcolor=blue,
     }

\title{CV - Vazha Dvalishvili}
\author{Scismic: The Talent Matching Platform for The Life Sciences (www.scismic.com)}
\date{May 2020}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Vazha Dvalishvili}
\cvpersonalinfo{
\faEnvelope \hspace{1mm} \href{mailto:vazhadvalishvili@gmail.com}{vazhadvalishvili@gmail.com}  \hspace{1mm}
\faMobile* \hspace{1mm} \href{tel:+995551001678}{+995551001678}  \hspace{1mm}
\faLinkedin \hspace{1mm} \href{https://www.linkedin.com/in/vazha-dvalishvili/}{LinkedIn} \hspace{1mm}
\faGithub \hspace{1mm}  \href{https://github.com/Vazhadval} {GitHub}
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Summary}
\begin{itemize}
\item NET developer with a strong focus on clean, efficient code, and a proven ability to solve complex problems.
\end{itemize}
 
 \section{Experience}

\cvsubsection{Intermedia}[Remote, Georgia]
[Software Developer][January 2024 - present]

\begin{itemize}
\item 
I work with a small team in our company, focusing on a dedicated part of our large application where we handle the creation of quotes for end users, providing them with a range of equipment and service options. My role: back-end development, writing UI tests using Selenium/Playwright, and overseeing test builds and pipelines.

\end{itemize}

\cvsubsection{63 Bits}[Tbilisi, Georgia]
[.Net Developer][October 2022 - January 2024]

\begin{itemize}
\item With a team of 2 developers, built a fully(almost) automated warehouse system for one of the German companies(NeoIntralogistics GmbH) powered by robots, minimizing the need for human interaction and reducing manual processing time by 70\% through automation of warehouse workflows. 
\end{itemize}
\begin{itemize}
\item Wrote several applications for one of the largest companies in Georgia: Vian (former Evex). One of the challenging tasks was to implement logic to match payments to invoices. (with millions of rows in the database)
\end{itemize}

\cvsubsection{Flatrock Technology}[Remote, Georgia]
[.Net Developer][October 2021 - October 2022]

\begin{itemize}
\item Projects: IT talent hiring platform. Role: back-end API development and "Evaluation Tool" - automation tool for hiring new employees. Role: full-stack developer. Technologies:.Net + React. 
\end{itemize}

%% Another custom command provide by scimisc-cv.sty.
%% First two argumetns are typeset on the first line in bold; 3rd and 4th arguments are typset on second line in italics. 2nd, 3rd and 4th arguments are OPTIONAL
\cvsubsection{PayUnicard}[Tbilisi, Georgia]
[.Net Developer][August 2020 - October 2021]

\begin{itemize}
\item Building the online bank application, where my role was as a back-end developer focusing mainly on building API.
\end{itemize}
\begin{itemize}
\item Created several web applications for loyalty programs for different companies.
\end{itemize}

%% An example of leaving an argument empty


\cvsubsection{Webiz}[Tbilisi, Georgia]
[.Net Developer/Test automation engineer ][August 2019 - August 2020]

\begin{itemize}
\item I began as a Test Automation Engineer with Selenium in C\#, then moved into .NET backend development, working on an e-commerce application where I analyzed existing code and implemented new features.
\end{itemize}

 
\section{Education}

\begin{itemize}
\item .NET Core, MVC, Razor Pages, WebAPI,Microservices architecture, React - Udemy, 2020
\item Programming methodology - Stanford online course, 2019
\item C\#, .NET, MS SQL - Personal mentorship (Davit Dvali - Group-based training) 2019-2020
\item Bachelors, Business Administration, Tbilisi State University, 2012 - 2016  
\item Physics and Mathematics school of Kutaisi, 2012
\end{itemize}
 

\section{Projects}

\begin{itemize}
\item Comfort Room - I build everything from scratch and currently implementing new features 
\href{https://comfortroom.ge }{comfortroom.ge}. 
\item Microservices Test Project - Used Technologies: .NET 5, EF Core,Dapper, MS SQL, mongo db, postgres,redis, rabbitMQ, gRPC, docker... Link : \href{https://github.com/Vazhadval/MicroservicesProject}{Microservices}.
\item Book Store - My first "Big" .net core application with full E-commerce functionality. (user, product, payment management) \href{https://www.github.com/Vazhadval/BookStore}{BookStore}.


\end{itemize}



\section{Skills}

\begin{description}[widest=Langauges]
\item[Personal:] Logic, Research, Team player, communication/explanation, ability to use AI tools effectively 
\item[Languages:]	English, Georgian(native).
\item [Tech Stack:] C\#, .NET (WebAPI, MVC, Razor...), Entity Framework, MS SQL, JavaScript, React
\end{description}

\vspace{3mm}
\section{Hobbies}
  \faMusic \hspace{1mm} Music\hspace{1mm} 
  \faChessKnight \hspace{1mm} Chess \hspace{1mm} 
  \faFutbol \hspace{1mm} Football \hspace{1mm} 
  \faCode \hspace{1mm} Algorithms \hspace{1mm} 
  \faGamepad \hspace{1mm} Videogames \hspace{1mm} 
  \faYoutube \hspace{1mm} Posting educational videos on YouTube
\end{document}
